---
title: '1.1'
output: html_document
---


```{r}
library(tidyverse)
library(ggplot2) # Data visualization
library(readr) # CSV file I/O, e.g. the read_csv function
library(dplyr)
library(data.table)
library(stringr)
library(splitstackshape)
library(ggrepel)
library(highcharter)
library(sqldf)
library(formattable)
library(gtools)
library(rpart)
library(flexclust)
```



```{r}
database <- read_csv("database.csv")
meta <- read_csv("movie_metadata.csv")
credits <- read_csv("tmdb_5000_credits.csv")
movies <- read_csv("tmdb_5000_movies.csv")
```

## remove trailing spaces, special characters, duplicates

```{r}
mytrimfunction <- function (x) gsub("^\\s+|\\s+$", "", x)
meta$movie_title <- mytrimfunction(meta$movie_title)
meta$movie_title <- mytrimfunction(gsub("Â", "", meta$movie_title))
meta <- meta[!duplicated(meta$movie_title),]
meta$movie_title <- str_trim(meta$movie_title)
```

## changing years from 1927/1928 to 1927
```{r}
AwYear = data.table(database$Year)
AwYear = cSplit(as.data.table(AwYear$V1), "V1", "/") 
names(AwYear)[1] <- "Year"
AwYear$V1_2 <- NULL
database$Year = AwYear$Year
```


## plot number of nomination by year (attention to regulation after 1945 min 99 max 130)

```{r}
tyears <- database %>% group_by(Year) %>% summarise(Total = n()) %>% arrange(desc(Total))

TyrNomPlot =  ggplot(tyears)+ geom_point(aes(Year, Total), size = 4, color = 'grey') +
                geom_label_repel(aes(Year, Total, fill = factor(Total), label = Total),
                  fontface = 'bold', color = 'white', box.padding = unit(0.35, "lines"),
                  point.padding = unit(0.5, "lines"),segment.color = 'grey50')+
                ggtitle("Total number of nominations by year")+ labs(x="Year",y="Total Nominations") +
                scale_x_continuous(breaks = scales::pretty_breaks(n = 10)) +
                scale_y_continuous(breaks = scales::pretty_breaks(n = 20)) +
                labs(fill = "Nominations") + theme(legend.title = element_text(face = "bold", size = 14)) + 
                theme(axis.text=element_text(size=14), axis.title=element_text(size=20,face="bold"))
TyrNomPlot
```

```{r}
NomNWins <- database %>% group_by(Award) %>% summarise(n = n()) %>%  arrange(-n) %>% glimpse() 

TreeAwCategs = hchart(NomNWins, "treemap", hcaes(x = Award, value = n, color = n))%>%
      hc_add_theme(hc_theme_google()) %>% hc_title(text = "Academy award categories and total nominations") %>%
      hc_credits(enabled = TRUE, text = "Sources: Academy of Motion Picture Arts and Sciences", 
                 style = list(fontSize = "12px"))

TreeAwCategs
```

## select database

```{r}

best.pict <- filter(database,Award=="Best Picture")


best.pict[is.na(best.pict)] <- 0

sum(best.pict$Winner)

colnames(best.pict)[5] <- "movie_title"


df <- inner_join(best.pict, meta)

```

## Country nominated

```{r}
c <- df %>% group_by(country) %>% count() %>% arrange(desc(n))

TreeAwCategs = hchart(c, "treemap", hcaes(x = country, value = n, color = n))%>%
      hc_add_theme(hc_theme_google()) %>% hc_title(text = "Academy award categories and total nominations") %>%
      hc_credits(enabled = TRUE, text = "Sources: Academy of Motion Picture Arts and Sciences", 
                 style = list(fontSize = "12px"))

TreeAwCategs
```

## duration

```{r}

newdf %>% group_by(duration) %>% count() %>% arrange(desc(n))

newdf %>% group_by(Winner) %>%
  ggplot(aes(x = as.factor(nominee) , y = duration)) +
  geom_boxplot() +
  theme(axis.text.x = element_text(angle = 90, vjust = 0.3, hjust = 1), plot.title = element_text(hjust = 0.5), plot.subtitle = element_text(hjust = 0.5)) +
  labs(title = "Duration for nominee or not",  x = "0 = Non nominee 1 = Nominee", y = "Duration (min)") +
  scale_color_gradient(low = "green", high = "red")

```

## budget

```{r}

newdf %>% group_by(budget) %>% count() %>% arrange(desc(n))

newdf %>% group_by(Winner) %>%
  ggplot(aes(x = as.factor(nominee) , y = budget)) +
  geom_boxplot() +
  theme(axis.text.x = element_text(angle = 90, vjust = 0.3, hjust = 1), plot.title = element_text(hjust = 0.5), plot.subtitle = element_text(hjust = 0.5)) +
  labs(title = "Budget for nominee or not",  x = "0 = Non nominee 1 = Nominee", y = "Budget") +
  scale_color_gradient(low = "green", high = "red")
```

## PG rating

```{r}

df %>% group_by(content_rating) %>% count() %>% arrange(desc(n))

```


## number of nommination by genre

```{r}

tmp1 <- df

genrestmp <- tmp1[tmp1$genres != "", ]
genres <- c()
i <- 1
for (genr in genrestmp$genres){
    kw <- strsplit(genr, "[|]")
    if (length(kw) != 0){
        for (word in kw[[1]]){
            if (!(word %in% genres)){
                genres[i] <- word
                i = i + 1
            }
        }
    }
}

oscarweight <- rep(0, length(genres))
genresoscars <- data.frame(genres, oscarweight)
rm(i)
for(i in 1:nrow(genresoscars)) {
    irow <- genresoscars[i,]

    for(j in 1:nrow(tmp1)) {
        jrow <- tmp1[j,]

        if (grepl(irow$genres, jrow$genres)) {
            genresoscars[i,]$oscarweight = genresoscars[i,]$oscarweight + 1
        }
    }
}
genresoscars <- genresoscars %>% select(genres, oscarweight) %>% arrange(desc(oscarweight))
genresoscars$ID <- seq.int(nrow(genresoscars))
genresoscars <- genresoscars[c(3, 1, 2)]
setnames(genresoscars, old=c("ID", "genres", "oscarweight"), new=c("Sl. No.", "Genres", "Oscar Weightage"))
genresoscars %>% formattable(list("Oscar Weightage" = color_bar("lightblue")), align = 'l')


## open the table in new window


```



## number of nomination by key words 


```{r}
tmp1 <- df

keywordstmp <- tmp1[tmp1$genres != "", ]
keywords <- c()
i <- 1
for (keyw in genrestmp$plot_keywords){
    kw <- strsplit(keyw, "[|]")
    if (length(kw) != 0){
        for (word in kw[[1]]){
            if (!(word %in% keywords)){
                keywords[i] <- word
                i = i + 1
            }
        }
    }
}
oscarweight <- rep(0, length(keywords))
keywordsoscars <- data.frame(keywords, oscarweight)
rm(i)

for(i in 1:nrow(keywordsoscars)) {
    irow <- keywordsoscars[i,]

    for(j in 1:nrow(tmp1)) {
        jrow <- tmp1[j,]

        if (grepl(irow$keywords, jrow$plot_keywords)) {
            keywordsoscars[i,]$oscarweight = keywordsoscars[i,]$oscarweight + 1
        }
    }
}
keywordsoscars <- keywordsoscars %>% select(keywords, oscarweight) %>% arrange(desc(oscarweight))
keywordsoscars$ID <- seq.int(nrow(keywordsoscars))
keywordsoscars <- keywordsoscars[c(3, 1, 2)]
setnames(keywordsoscars, old=c("ID", "keywords", "oscarweight"), new=c("Sl. No.", "Keywords", "Oscar Weightage"))
keywordsoscars %>% formattable(list("Oscar Weightage" = color_bar("lightblue")), align = 'l')
```



## now bubble chart of the combination of keyword and genre

```{r}
keywordsoscars$oscarweight = 0
topgenres <- genresoscars[1:12,]
topkeywords <- keywordsoscars[1:15,]
topGK = merge(x = topgenres, y = topkeywords, by = NULL)
topGK$"Sl. No..x" <- NULL
topGK$"Sl. No..y" <- NULL
topGK$"Oscar Weightage.x" <- NULL
topGK$"Oscar Weightage.y" <- NULL
weight <- rep(0, dim(topGK)[1])
count <- rep(0, dim(topGK)[1])
topGK <- data.frame(topGK, weight, count)
for(i in 1:nrow(topGK)) {
    irow <- topGK[i,]

    for(j in 1:nrow(tmp1)) {
        jrow <- tmp1[j,]

        if (grepl(irow$Genres, jrow$genres) & grepl(irow$Keywords, jrow$plot_keywords)) {
            topGK[i,]$weight = topGK[i,]$weight + 1
            topGK[i,]$count = topGK[i,]$count + 1
        }
    }
}
topGK <- topGK %>% select(Genres, Keywords, weight, count) %>% arrange(desc(weight))
topGK$ID <- seq.int(nrow(topGK))
topGK <- topGK[c(5, 1, 2, 3, 4)]
setnames(topGK, old=c("ID", "weight", "count"), new=c("SlNo", "Weightage", "Count"))
scplot <- ggplot(topGK, aes(x = Keywords, y = Genres, size = Weightage, fill = Count)) +
        geom_point(shape = 21) + theme(axis.text.x = element_text(angle = 45, vjust = 0.65))
scplot
```



# Now with use machine learning to predict nominees

## first use new data base and make a train and a test set

```{r}
df <- df %>% mutate(nominee = 1)

## add now the same number of row with movie that were not nominated so we have an homogenous dataset to make the train and test

notindf <- subset(meta, !(movie_title %in% df$movie_title))

notindf <- notindf[complete.cases(notindf),]

notindf <- notindf[sample(nrow(notindf), 800), ]



newdf <- bind_rows(df, notindf)

newdf$nominee[is.na(newdf$nominee)] <- 0



library(Amelia)
missmap(newdf, main = "Missing values vs observed")


newdf$budget[is.na(newdf$budget)] <- mean(newdf$budget,na.rm=T)

newdf <- newdf[complete.cases(newdf$gross),]

missmap(newdf, main = "Missing values vs observed")

train <- newdf[sample(nrow(newdf), 800), ]

test <- subset(newdf, !(movie_title %in% train$movie_title))

```


## now we can train test and score our model 

## start with a logistice regression since we want to now if movie is nominated or not. 

```{r}

## maybe put genre and key word in one col for each word

## var to add : genres, plot_keywords,director_name,actor_2_name,actor_3_name,actor_1_name, country,content_rating
## add  : gross - budget , imdb_score, movie_facebook_likes, cast_total_facebook_likes
model <- glm(nominee ~ duration+gross+budget+imdb_score+movie_facebook_likes+cast_total_facebook_likes,family=binomial(link='logit'),data=train)



summary(model)

anova(model, test="Chisq")

library(pscl)
pR2(model)

## now test the model 

fitted.results <- predict(model,newdata=test,type='response')
fitted.results <- ifelse(fitted.results > 0.5,1,0)




misClasificError <- mean(fitted.results != test$nominee)

print(paste('Accuracy',1-misClasificError))



model2 <- step(model)

summary(model2)

anova(model2, test="Chisq")

fitted.results2 <- predict(model2,newdata=test,type='response')
fitted.results2 <- ifelse(fitted.results2 > 0.5,1,0)
misClasificError2 <- mean(fitted.results2 != test$nominee)
print(paste('Accuracy',1-misClasificError))
print(paste('Accuracy2',1-misClasificError2))
```


## Classification tree



```{r}
fit <- rpart(nominee ~ duration+gross+budget+imdb_score+movie_facebook_likes+cast_total_facebook_likes,
  	method="class", data=train)
printcp(fit)
plotcp(fit)
#summary(fit)

plot(fit, uniform=TRUE, 
  	main="Classification Tree for Awards Nominees")
text(fit, use.n=TRUE, all=TRUE, cex=.8)


# prune the tree 
pfit<- prune(fit, cp=   fit$cptable[which.min(fit$cptable[,"xerror"]),"CP"])

# plot the pruned tree 
plot(pfit, uniform=TRUE, 
  	main="Pruned Classification Tree for Awards Nominees")
text(pfit, use.n=TRUE, all=TRUE, cex=.8)


pred <- predict(fit, newdata = test, type= "class")
pred2 <- predict(pfit, newdata = test, type= "class")


misClasificError <- mean(pred != test$nominee)
misClasificError2 <- mean(pred2 != test$nominee)

print(paste('Accuracy',1-misClasificError))
print(paste('Accuracy2',1-misClasificError2))
```

## K-mean method

```{r}


cl = kcca(train$nominee, k=2, kccaFamily("kmeans"))

cl

cl1 = kcca(select(train, duration,gross,budget,imdb_score,movie_facebook_likes,cast_total_facebook_likes ), k=2, kccaFamily("kmeans"))
cl1



pred_train <- predict(cl1)
pred_test <- predict(cl1, newdata=select(test, duration,gross,budget,imdb_score,movie_facebook_likes,cast_total_facebook_likes ))


image(cl1)
points(select(train, duration,gross,budget,imdb_score,movie_facebook_likes,cast_total_facebook_likes ), col=pred_train, pch=19, cex=0.3)
points(select(test, duration,gross,budget,imdb_score,movie_facebook_likes,cast_total_facebook_likes ), col=pred_test, pch=22, bg="orange")
```




## test for removing non existing factor between test and train (if appears in test then set to NA)


```{r}
remove_missing_levels <- function(fit, test_data) {
  library(magrittr)
  
  # https://stackoverflow.com/a/39495480/4185785
  
  # drop empty factor levels in test data
  test_data %>%
    droplevels() %>%
    as.data.frame() -> test_data
  
  # 'fit' object structure of 'lm' and 'glmmPQL' is different so we need to
  # account for it
  if (any(class(fit) == "glmmPQL")) {
    # Obtain factor predictors in the model and their levels
    factors <- (gsub("[-^0-9]|as.factor|\\(|\\)", "",
                     names(unlist(fit$contrasts))))
    # do nothing if no factors are present
    if (length(factors) == 0) {
      return(test_data)
    }
    
    map(fit$contrasts, function(x) names(unmatrix(x))) %>%
      unlist() -> factor_levels
    factor_levels %>% str_split(":", simplify = TRUE) %>%
      extract(, 1) -> factor_levels
    
    model_factors <- as.data.frame(cbind(factors, factor_levels))
  } else {
    # Obtain factor predictors in the model and their levels
    factors <- (gsub("[-^0-9]|as.factor|\\(|\\)", "",
                     names(unlist(fit$xlevels))))
    # do nothing if no factors are present
    if (length(factors) == 0) {
      return(test_data)
    }
    
    factor_levels <- unname(unlist(fit$xlevels))
    model_factors <- as.data.frame(cbind(factors, factor_levels))
  }
  
  # Select column names in test data that are factor predictors in
  # trained model
  
  predictors <- names(test_data[names(test_data) %in% factors])
  
  # For each factor predictor in your data, if the level is not in the model,
  # set the value to NA
  
  for (i in 1:length(predictors)) {
    found <- test_data[, predictors[i]] %in% model_factors[
      model_factors$factors == predictors[i], ]$factor_levels
    if (any(!found)) {
      # track which variable
      var <- predictors[i]
      # set to NA
      test_data[!found, predictors[i]] <- NA
      # drop empty factor levels in test data
      test_data %>%
        droplevels() -> test_data
      # issue warning to console
      message(sprintf(paste0("Setting missing levels in '%s', only present",
                             " in test data but missing in train data,",
                             " to 'NA'."),
                      var))
    }
  }
  return(test_data)
}
## maybe put genre and key word in one col for each word

## var to add : genres, plot_keywords,director_name,actor_2_name,actor_3_name,actor_1_name, country,content_rating

model <- glm(nominee ~ duration+budget,family=binomial(link='logit'),data=train)


summary(model)

anova(model, test="Chisq")

library(pscl)
pR2(model)


## now test the model 


fitted.results <- predict(model,newdata = remove_missing_levels(fit = model, test_data = test),type='response')
fitted.results <- ifelse(fitted.results > 0.5,1,0)

misClasificError <- mean(fitted.results != test$nominee)
print(paste('Accuracy',1-misClasificError))
```



























