---
title: "Course work"
author: "Antoine Fama"
date: "30 mai 2018"
output: html_document
---


#Introduction

- An introduction to the context or background of the topic
- Research questions: what do we want to study?
- Motivation, why did we do this; why this is important interesting
- Introducing used new concepts/terminology (if needed)
- Introducing the main ideas and used methodology
- Briefly introduce the results


#Data sources

<!-- Give a detailed description of used data sources and analysis data sets in this section.   -->
<!-- Tables can be used to list data items (name, description, data type, etc.) -->

We will use....

```{r dataimport, include=FALSE}
database <- read_csv("database.csv")
meta <- read_csv("movie_metadata.csv")
```

<!-- remove trailing spaces, special characters, duplicates -->
```{r clean1, include=FALSE}
mytrimfunction <- function (x) gsub("^\\s+|\\s+$", "", x)
meta$movie_title <- mytrimfunction(meta$movie_title)
meta$movie_title <- mytrimfunction(gsub("Â", "", meta$movie_title))
meta <- meta[!duplicated(meta$movie_title),]
meta$movie_title <- str_trim(meta$movie_title)
```
<!-- changing years from 1927/1928 to 1927 -->
```{r clean2, include=FALSE}
AwYear = data.table(database$Year)
AwYear = cSplit(as.data.table(AwYear$V1), "V1", "/") 
names(AwYear)[1] <- "Year"
AwYear$V1_2 <- NULL
database$Year = AwYear$Year
```


After some basic transformation, our two datasets look like:

```{r}
database %>% head(n = 1) %>% kable(format = "latex", booktabs = TRUE)
```

```{r}
panderOptions('table.continues', '')
pander(head(meta,n=10), split.cell = 140, split.table = 140)
```




#Data analysis

##Descriptive analysis

<!-- Simple summaries, graphs, etc. -->


##Data cube

<!-- A multidimensional cube (table) presentation of (a suitable part of) the data set. -->


##Statistical/Data mining analysis

<!-- Using at least two statistical / data mining methods to study the data. -->
<!-- - Describing the methods -->
<!-- - Explaining why the methods are suitable for this task -->
<!-- - Illustrating and explaining the results using plots, tables and text. -->


#Conclusion

<!-- - Offer a brief summary of the study -->
<!-- - Offer your conclusions/implications of the findings -->
<!-- - How the results can could be applied in practice? (if suitable for the topic) -->
<!-- - Describe the limitations of the study -->